A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-09 paper.tex
comment edits

\todo[inline]{JS: In the above you've lumped proxy-based and blame
  tracking together, which is incorrect. AFAIK,
  \cite{findler2002contracts} is the origin of blame tracking. AFAIK,
  \citet{Breazu-Tannen:1990vc} is the origin of proxy-based
  casts. (Who knows, there could be an even earlier paper for
  proxy-based casts, but that's the earliest one I know.)
  \citet{herman2010space} cited the wrong paper for function proxies,
  perhaps because they didn't know about the decade earlier
  \citet{Breazu-Tannen:1990vc}. Also, \cite{findler2002contracts}
  should have cited \citet{Breazu-Tannen:1990vc} but did not. Perhaps
  because they did not consider that papers about ``casts'' to be
  closely related to their paper about ``contracts''.  Or perhaps they
  too did not know about \citet{Breazu-Tannen:1990vc}.  Authors make
  mistakes all the time regarding related work, and this is just yet
  another example of that. For that matter, I should have cited
  \citet{Breazu-Tannen:1990vc} in \citet{siek2006gradual} but did not,
  probably because I had learned about it from the TAPL textbook
  (section 15.6) and therefore thought it was so standard that it
  didn't need a citation.  But it would have been better for me to
  cite it.}

>>>>

\todo[inline]{JS: In the above you've lumped proxy-based and blame
  tracking together, which is incorrect. AFAIK,
  \cite{findler2002contracts} is the origin of blame tracking. AFAIK,
  \citet{Breazu-Tannen:1990vc} is the origin of proxy-based casts.
  You can read both papers for yourself and be the judge.  BTW, TAPL
  (section 15.6) cites Breazu-Tannen.  So \citet{herman2010space}
  cited the wrong paper for function proxies, perhaps because they
  didn't know about \citet{Breazu-Tannen:1990vc}. Also,
  \cite{findler2002contracts} should have cited
  \citet{Breazu-Tannen:1990vc} but did not. Perhaps because they did
  not consider that papers about ``casts'' to be closely related to
  their paper about ``contracts''.  Or perhaps they too did not know
  about \citet{Breazu-Tannen:1990vc}.  Authors make mistakes all the
  time regarding related work, and this is just yet another example of
  that. For that matter, I should have cited
  \citet{Breazu-Tannen:1990vc} in \citet{siek2006gradual} but did not,
  probably because I had learned about it from TAPL and therefore
  thought it was so standard that it didn't need a citation.  But it
  would have been better for me to cite it.}
